---
title: "FinalProject"
author: "Yuxuan Wang"
date: "2022-12-10"
output:
  pdf_document: default
  html_document: default
---

Loading packages

```{r}
library(topicmodels)
library(slam)
library(ggplot2)
library(MASS)
library(faraway)
```

Implementing LDA. The data are constructed from python. You should run Final_python.ipynb before running this file.

```{r}
ii=read.table('result_data/i.txt')
i1=as.matrix(ii)
jj=read.table('result_data/j.txt')
j1=as.matrix(jj)
vv=read.table('result_data/v.txt')
v1=as.matrix(vv)
dim(v1)<-c(3502965,1)
v1=as.vector(v1)
theMatrix=simple_triplet_matrix(i=i1,j=j1,v=v1) 
LDA_object = LDA(theMatrix,10, method = "Gibbs", control= NULL, model = NULL)
topic = LDA_object@gamma
topic_prob = LDA_object@beta
save(LDA_object,file='result_data/LDA_k10.Rdata')
write.csv(topic,file='result_data/LDA.csv')
write.csv(t(topic_prob), 'result_data/topics_k10.csv')
```

After sentiment analysis by python and LDA by R, we now have all dependent variables.
Now we can start to construct the data frame energy, information, desicion, lifestyle as the four axis of 16 MBTI type.

```{r}
target = read.table('result_data/mbti_target.csv')
sentiment = read.table("result_data/sentiment.csv", sep = ',')
Energy = rep(0, dim(target)[1])
Information = rep(0, dim(target)[1])
Decision = rep(0, dim(target)[1])
Lifestyle = rep(0, dim(target)[1])
for (i in 1: 8673){
  mbti <- target[i,]
  Energy[i] <- (substr(mbti, 1, 1) == 'E')
  Information[i] <- (substr(mbti, 2, 2) == 'S')
  Decision[i] <- (substr(mbti, 3, 3) == 'T')
  Lifestyle[i] <- (substr(mbti, 4, 4) == 'J')
}
```

Start building model and select dependent variables for Energy axis model.

```{r}
df_E = data.frame(topics = topic, mbti = Energy, sentiment = sentiment)
col_names = c("Topic1", "Topic2", "Topic3", "Topic4", "Topic5", "Topic6", "Topic7", "Topic8", "Topic9", "Topic10", "Energy", "neg", "pos")
colnames(df_E) = col_names
modelE = glm(Energy~.-Topic10, data = df_E, family = binomial(link = "logit"))
modelE_final = glm(Energy~.-Topic2-Topic4-Topic6-neg-Topic10, data = df_E, family = binomial(link = "logit"))
#summary(modelE)
BIC(modelE)
BIC(modelE_final)
summary(modelE_final)
confint(modelE_final)
```

Start building model and select dependent variables for Information axis model.

```{r}
df_I = data.frame(topics = topic, mbti = Information, sentiment = sentiment)
col_names = c("Topic1", "Topic2", "Topic3", "Topic4", "Topic5", "Topic6", "Topic7", "Topic8", "Topic9", "Topic10", "Information", "neg", "pos")
colnames(df_I) = col_names
modelI = glm(Information~.-Topic10, data = df_I, family = binomial(link = "logit"))
#summary(modelI)
BIC(modelI)
modelI_final = glm(Information~.-neg-Topic10, data = df_I, family = binomial(link = "logit"))
BIC(modelI_final)
summary(modelI_final)
```

Start building model and select dependent variables for Decision axis model.

```{r}
df_D = data.frame(topics = topic, mbti = Decision, sentiment = sentiment)
col_names = c("Topic1", "Topic2", "Topic3", "Topic4", "Topic5", "Topic6", "Topic7", "Topic8", "Topic9", "Topic10", "Decision", "neg", "pos")
colnames(df_D) = col_names
modelD = glm(Decision~.-Topic10, data = df_D, family = binomial(link = "logit"))
modelD_final = glm(Decision~.-neg-Topic10, data = df_D, family = binomial(link = "logit"))
#summary(modelD)
BIC(modelD)
BIC(modelD_final)
summary(modelD_final)
```

Start building model and select dependent variables for Lifestyle axis model.

```{r}
df_L = data.frame(topics = topic, mbti = Lifestyle, sentiment = sentiment)
col_names = c("Topic1", "Topic2", "Topic3", "Topic4", "Topic5", "Topic6", "Topic7", "Topic8", "Topic9", "Topic10", "Lifestyle", "neg", "pos")
colnames(df_L) = col_names
modelL = glm(Lifestyle~.-Topic10, data = df_L, family = binomial(link = "logit"))
modelL_final = glm(Lifestyle~.-neg-pos-Topic1-Topic4-Topic7-Topic10, data = df_L, family = binomial(link = "logit"))
#summary(modelL_final)
BIC(modelL)
BIC(modelL_final)
summary(modelL_final)
```

Some plots for data check.

```{r}
plot(modelE_final, which = 4, id.n = 3, main = "")
```
```{r}
halfnorm(rstudent(modelE_final))
```
Data check

```{r}
anova(modelE_final,modelE)
anova(modelI_final,modelI)
anova(modelD_final,modelD)
anova(modelL_final,modelL)
```

